

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={blue!50!black},
    urlcolor={black}
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}


  \textbf{{\LARGE Rohtih BN}} & Email: \href{mailto:rohithbn27@gmail.com}{rohithbn27@gmail.com}\\
  \underline{\href{https://rohith-portfolio-theta.vercel.app}{Portfolio}} & \underline{\href{https://www.linkedin.com/in/rohith-bn-b9485b318/}{LinkedIn}} \\
  \underline{\href{https://github.com/RohithBN}{Github: RohithBN}} & Mobile:~~~+91-861-829-4710
\end{tabular*}


	    

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Dayananda Sagar College Of Engineering}{CGPA: 9.72}
      {Bachelor of Engineering-Information Science Engineering }{2022 - 2026}
      \resumeSubheading
        {Kumarans PU College}{CGPA: 9.82}
      {12th Standard }{2020 - 2022}
      \vspace{-5pt}
    \resumeSubHeadingListEnd
	   \vspace{-5pt}
\section{Technical Skills}
\vspace{2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, C++, Go}

\textbf{Technologies/Frameworks}{: React, Next.js, Node.js}

\textbf{Databases/Tools}{: MongoDB, PostgreSQL, Appwrite, MySQL, Firebase}
}}
 \end{itemize}


\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RootsGoods}{Dec 2024 – Mar 2025}
      {AI Intern}{Bengaluru, India}
      \begin{itemize}
        \item Built a time-series forecasting model using Bidirectional LSTM (Bi-LSTM) architecture to predict maize prices across various markets in Karnataka.
        \item Collected and organised a comprehensive dataset with over 15,000 rows of historical maize prices across all major market locations.
      \end{itemize}
  \resumeSubHeadingListEnd



 
  
%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{\textbf{PeerCast} $|$ \emph{React, WebRTC, Go, Tailwind CSS} $|$
\textmd{\href{https://github.com/RohithBN/Video-chat-app}{\underline{GitHub}}}
}
{
\begin{itemize}
\item Built a real-time communication platform using React, WebRTC, and Go with features like video/audio calls, chat, file sharing, and screen sharing.
\item Implemented a Go-based signaling server with dynamic room creation and seamless peer connection management.
\item Enabled secure, chunked file transfer, real-time messaging, and privacy-focused controls.
\end{itemize}
}

\resumeSubItem{\textbf{OpusAI} $|$ \emph{Next.js, Clerk, Firebase, NeonDB, Vapi, Gemini, shadcn} $|$ 
\textmd{\href{https://github.com/RohithBN/AI-Coach}{\underline{GitHub}}}
}
{
\begin{itemize}
\item Built a responsive web app for AI-powered mock interviews with real-time voice interaction via Vapi and feedback using Google Gemini..
\item Integrated Clerk auth and Firebase for personalized dashboards, resume-based Q\&A, and career chatbot.
\item Added job search with dynamic FAQs, resume tools, and analytics-based interview feedback.
\end{itemize}
}

\resumeSubItem{\textbf{DNS Server Implementation} $|$ \emph{Go, UDP, DNS Protocol} $|$
\textmd{\href{https://github.com/RohithBN/DNS}{\underline{GitHub}}}
}
{
\begin{itemize}
\item Developed a lightweight DNS server in Go that efficiently handles DNS queries with support for multiple record types (A, AAAA, NS, CNAME, MX, TXT) and implements recursive resolution.
\item Engineered a robust fallback mechanism utilizing multiple DNS providers (Google DNS, Cloudflare, Quad9) ensuring 99.9\% query resolution reliability.
\item Implemented modular architecture separating concerns (headers, questions, records, resolver) for improved maintainability and testability, with comprehensive unit tests achieving 90\% code coverage.
\end{itemize}
}

\resumeSubHeadingListEnd






% %-----------LICENSE AND CERTIFICATIONS-----------------
 \vspace{-10pt}
\section{ACHIEVEMENTS AND CERTIFICATIONS}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeSubItem{First Place in Open League Track at Blitz'24 hosted by IEDC DSCE}{}
\vspace{2pt}
\resumeSubItem{Complete web development course - October 2024}{}
\vspace{2pt}
\resumeSubItem{Python Fundamentals $|$  Infosys $|$  Springboard - August 2023}{}
\vspace{2pt}
\resumeSubHeadingListEnd
\vspace{-5pt}



     \section{COMMUNITY EXPERIENCE}
\resumeSubHeadingListStart
    \resumeSubheading
        {LITSOC, DSCE}{Bengaluru, India}
        {Member of the Literary Society of Dayananda Sagar College Of Engineering.}{Jan 2023-Present}
    \resumeSubheading
        {Public Speaking Association, DSCE}{Bengaluru, India}
        {Head of the Official Public Speaking Association of Dayananda Sagar College of Engineering.}{July 2024-Present}
        \newline 
        \textit{Won multiple competitions and performed for crowds varying from 20-200}
\resumeSubHeadingListEnd



\end{document}
